Plot responses to model covariates to inform threshold choices for VOCC

### 2019-08-27 analysis/VOCC/3-fixed-var-response-plots.Rmd
make optimal values of temp and do based on fixed effect rather than time-varying models

Species
```{r}
# species <- params$species
# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
 species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds

@@

Choose model details
```{r}
# covariates <- "+muddy+mixed+rocky"
# covariates <- "+mixed+rocky"
covariates <- "+muddy+any_rock"
# covariates <- "+trawled+muddy+rocky+mixed"
# covariates <- "+trawled+mixed+rocky"
# covariates <- "+trawled+mixed"
```

@@

Load Dissolved O2 models
```{r}
rm(
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- TRUE
# covariates <- ""

@@

  adult_survey_all <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey_all <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey_all")) adult_survey_all <- NULL
if (!exists("imm_survey_all")) imm_survey_all <- NULL

@@

  adult_survey1 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey1 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey1")) adult_survey1 <- NULL
if (!exists("imm_survey1")) imm_survey1 <- NULL

@@

  adult_survey4 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey4 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey4")) adult_survey4 <- NULL
if (!exists("imm_survey4")) imm_survey4 <- NULL

@@

  adult_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})

@@

model_list <- list(
  adult_survey_all = adult_survey_all, imm_survey_all = imm_survey_all,
  adult_survey1 = adult_survey1, imm_survey1 = imm_survey1,
  adult_survey4 = adult_survey4, imm_survey4 = imm_survey4,
  adult_survey16 = adult_survey16, imm_survey16 = imm_survey16
)

@@

Load temperature models
```{r}
rm(
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- TRUE
try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")

  adult_survey1 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey1 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey1")) adult_survey1 <- NULL
if (!exists("imm_survey1")) imm_survey1 <- NULL

@@

  adult_survey4 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey4 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey4")) adult_survey4 <- NULL
if (!exists("imm_survey4")) imm_survey4 <- NULL

@@

  adult_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})

@@

temp_model_list <- list(
  adult_survey1 = adult_survey1, imm_survey1 = imm_survey1,
  adult_survey4 = adult_survey4, imm_survey4 = imm_survey4,
  adult_survey16 = adult_survey16, imm_survey16 = imm_survey16
)

@@

for (i in seq_len(length(temp_model_list))) {
  td[[i]] <- time_varying_density(temp_model_list[[i]], predictor = "temp")
  #browser()
  if (length(td[[i]])>0) td[[i]]$model <- names(temp_model_list[i])
}

tdat <- do.call("rbind", td)

tdat <- tdat %>%
  group_by(model) %>%
  mutate(maxy = max(y_hat)) %>%
  ungroup() %>%
  mutate(meanymax = mean(maxy), sdymax = sd(maxy)) %>%
  filter(maxy < (meanymax + 2 * sdymax))

hist(tdat$maxy)

optimal_temp <- get_optimal_value(tdat, xlimits = c(3, 8))

@@

for (i in seq_len(length(model_list))) {
 do[[i]] <- time_varying_density(model_list[[i]], predictor = "do_mlpl")
 if (length(do[[i]])>0) do[[i]]$model <- names(model_list[i])
}
odat <- do.call("rbind", do)

odat <- odat %>%
  group_by(model) %>%
  mutate(maxy = max(y_hat)) %>%
  ungroup() %>%
  mutate(meanymax = mean(maxy), sdymax = sd(maxy)) %>%
  filter(maxy < (meanymax + 2 * sdymax))

hist(odat$maxy)

optimal_do <- get_optimal_value(odat, xlimits = c(0.5, 6))

date <- Sys.time()

params <- data.frame(species, optimal_do, optimal_temp, date)

other_params <- readRDS(paste0("data/optimal-values-by-species.rds"))
params <- rbind(other_params, params)
saveRDS(params, file = "data/optimal-values-by-species.rds")

@@

```{r}
d <- list()
do_plots <- list()
for (i in seq_len(length(model_list))) {
  d[[i]] <- time_varying_density(model_list[[i]], predictor = "do_mlpl")
  if (length(d[[i]]) == 0) {
    do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  } else {
    do_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Dissolved O2", xlimits = c(0, 8)) + ggtitle(paste(species, names(model_list[i])))
  }
}
print(do_plots)
```

@@

```{r}
d <- list()
temp_plots <- list()
for (i in seq_len(length(temp_model_list))) {
  d[[i]] <- time_varying_density(temp_model_list[[i]], predictor = "temp")

@@

  if (length(d[[i]]) == 0) {
    depth_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  } else {
    d[[i]]$x <- exp(d[[i]]$x)
    depth_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Depth", xlimits = c(0, 1000)) +
      ggtitle(paste(species, names(depth_model_list[i])))
  }
}
print(depth_plots)
```

>>>>

Species
```{r}
# species <- params$species
# # Species run so far...
 species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds

@@

Choose model details
```{r}
covariates <- ""
# covariates <- "+muddy+mixed+rocky"
# covariates <- "+mixed+rocky"
#covariates <- "+muddy+any_rock"
# covariates <- "+trawled+muddy+rocky+mixed"
# covariates <- "+trawled+mixed+rocky"
# covariates <- "+trawled+mixed"
```

@@

Load Dissolved O2 models
```{r}
rm(
  adult, imm,
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- FALSE
# covariates <- ""

@@

  adult <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult")) adult <- NULL
if (!exists("imm")) imm <- NULL

@@

  adult_survey1 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey1 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey1")) adult_survey1 <- NULL
if (!exists("imm_survey1")) imm_survey1 <- NULL

@@

  adult_survey4 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey4 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey4")) adult_survey4 <- NULL
if (!exists("imm_survey4")) imm_survey4 <- NULL

@@

  adult_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})

@@

model_list <- list(
  adult = adult, imm = imm,
  adult_survey1 = adult_survey1, imm_survey1 = imm_survey1,
  adult_survey4 = adult_survey4, imm_survey4 = imm_survey4,
  adult_survey16 = adult_survey16, imm_survey16 = imm_survey16
)

@@

Load temperature models
```{r}
rm(adult, imm,
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- FALSE
covariates <- "+muddy+any_rock"
covs <- gsub("\\+", "-", covariates)

  adult <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult")) adult <- NULL
if (!exists("imm")) imm <- NULL

  adult_survey1 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey1 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey1")) adult_survey1 <- NULL
if (!exists("imm_survey1")) imm_survey1 <- NULL

@@

  adult_survey4 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey4 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey4")) adult_survey4 <- NULL
if (!exists("imm_survey4")) imm_survey4 <- NULL

@@

  adult_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})

@@

temp_model_list <- list(
  adult = adult, imm = imm, 
  adult_survey1 = adult_survey1, imm_survey1 = imm_survey1,
  adult_survey4 = adult_survey4, imm_survey4 = imm_survey4,
  adult_survey16 = adult_survey16, imm_survey16 = imm_survey16
)

@@

for (i in seq_len(length(temp_model_list))) {
  td[[i]] <- fixed_density(temp_model_list[[i]], predictor = "temp")
  #browser()
  if (length(td[[i]])>0) td[[i]]$model <- names(temp_model_list[i])
  if (length(td[[i]])>0) td[[i]]$optimal_temp <- get_optimal_value(td[[i]], xlimits = c(0, 12))
}

tdat <- do.call("rbind", td) %>%
  group_by(model) %>%
  mutate(age = ifelse(grepl("imm", model), "imm", "adult"),
    t_maxy = max(y_hat)) %>% 
  select(model, age, optimal_temp, t_maxy) %>%
  distinct()

@@

for (i in seq_len(length(model_list))) {
 do[[i]] <- fixed_density(model_list[[i]], predictor = "do_mlpl")
 if (length(do[[i]])>0) do[[i]]$model <- names(model_list[i])
 if (length(do[[i]])>0) do[[i]]$optimal_do <- get_optimal_value(do[[i]], xlimits = c(0.5, 6))
}

odat <- do.call("rbind", do) %>%
  group_by(model) %>%
  mutate(age = ifelse(grepl("imm", model), "imm", "adult"),
    do_maxy = max(y_hat)) %>% 
  select(model, age, optimal_do, do_maxy) %>%
  distinct()

params <- full_join(tdat, odat, by=c("model", "age"))
#params <- tdat
params$species <- species
#params$date <- Sys.Date()

other_params <- readRDS(paste0("data/optimal-values-by-species-by-age.rds"))
params <- rbind(other_params, params)
saveRDS(params, file = "data/optimal-values-by-species-by-age.rds")

@@

```{r}
d <- list()
do_plots <- list()
for (i in seq_len(length(model_list))) {
  d[[i]] <- fixed_density(model_list[[i]], predictor = "do_mlpl")
  if (length(d[[i]]) == 0) {
    do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  } else {
    do_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Dissolved O2", xlimits = c(0, 8)) + ggtitle(paste(species, names(model_list[i])))
  }
}
print(do_plots)
```

@@

```{r}
d <- list()
temp_plots <- list()
for (i in seq_len(length(temp_model_list))) {
  d[[i]] <- fixed_density(temp_model_list[[i]], predictor = "temp")

@@

  if (length(d[[i]]) == 0) {
    depth_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  } else {
    d[[i]]$x <- exp(d[[i]]$x)
    depth_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Depth", xlimits = c(0, 800)) +
      ggtitle(paste(species, names(depth_model_list[i])))
  }
}
print(depth_plots)
```
